Digital History in Finland, 1488-1828

### 2016-10-04 inst/examples/manuscript-krakow.Rmd
Rmd update

  res <- titlecount_timeline(dfs, "gatherings", nmin = 15, mode = "n") 
  print(res$plot + ggtitle(paste(catal, " (n)", sep = "")))

  res <- titlecount_timeline(dfs, "gatherings", nmin = 15, mode = "percentage") 
  print(res$plot + ggtitle(paste(catal, " (%)", sep = "")))
}
```

>>>>

  res <- timeline(dfs, field = "titlecount", group = "gatherings", nmin = 15, mode = "absolute") 
  print(res$plot + ggtitle(paste(catal, " (n)", sep = "")))

  res <- timeline(dfs, field = "titlecount", group = "gatherings", nmin = 15, mode = "relative") 
  print(res$plot + ggtitle(paste(catal, " (%)", sep = "")))
}
```
